---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bnanalysis: [BirdNet Analyzer](https://github.com/kahst/BirdNET-Analyzer) in R

<!-- badges: start -->
```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

```{r, echo = FALSE, results='asis'}
cat(
	badge_lifecycle("experimental", "red"),
  badge_repostatus("Active", "green"),
  badge_license("GPL v3.0")
)
```
<!-- badges: end -->

## Description

bnanalysis is both a wrapper around [BirdNet Analyzer](https://github.com/kahst/BirdNET-Analyzer) and a tool for analyzing results derived from BirdNet. It allows users to run BirdNet directly from R. bnanalysis provides a collection of functions for installing, running BirdNet and analyzing BirdNet results. bnanalysis was developed as a tool to create a semi-automated analysis pipeline. 

* Features to-do list:
  + Support for operating systems other than Windows.
  + Function to create output tables for, for example, odd detections in Kaleidoscope or other.
  + Function for calculating VAR "Vocal Activity Rate"
  + Visualization functions for the bird community
  
bnanalysis is licensed under

## About

Developed by Andrew Fairbairn

<img src="https://raw.githubusercontent.com/FortAwesome/Font-Awesome/6.x/svgs/solid/house.svg" width="50" height="50"> https://afairbairn.com/
<img src="https://raw.githubusercontent.com/FortAwesome/Font-Awesome/6.x/svgs/solid/briefcase.svg" width="50" height="50"> [Chair for Terrestrial Ecology](https://www3.ls.tum.de/en/toek/home/), Technical University of Munich
<img src="https://raw.githubusercontent.com/FortAwesome/Font-Awesome/6.x/svgs/brands/researchgate.svg" width="50" height="50">
<img src="https://raw.githubusercontent.com/FortAwesome/Font-Awesome/6.x/svgs/brands/square-twitter.svg" width="50" height="50">



## Installation

You can install bnanalysis from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AFairbairn/bnanalysis")
```

## Example

This is a basic example which shows you how to install and use BirdNet:

```{r }
library(bnanalysis)

setwd("D:/myProject")

## Install BirdNet
getBN()

## Run BirdNet using default settings
## i is the input files path, as in BirdNet-Analyze
results <- analyze(i="D:/acoustic recordings")
head(results[,c(4:6)])
```
