---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chirpR: tools for automated acoustic analyses in R

<!-- badges: start -->
```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

```{r, echo = FALSE, results='asis'}
cat(
	badge_lifecycle("experimental", "red"),
	badge_github_actions("Afairbairn/chirpR"),
  badge_repostatus("Active", "green"),
  badge_license("CC BY-NC-SA 4.0")
)
```
<!-- badges: end -->

## Description

`chirpR` is an R package that simplifies the process of analyzing and interpreting bird acoustic monitoring data. It provides a user-friendly wrapper for [BirdNet-Analyzer](https://github.com/kahst/BirdNET-Analyzer) and [ecoVAD](https://github.com/NINAnor/ecoVAD), allowing users to easily install and run BirdNet and ecoVAD directly from R. Additionally, `chirpR` includes a collection of functions for analyzing and visualizing BirdNet output. Developed with a semi-automated analysis pipeline in mind, `chirpR` streamlines the analysis process.

## About

Developed by 🦜Andrew Fairbairn

Current lab: [Chair for Terrestrial Ecology](https://www3.ls.tum.de/en/toek/home/), Technical University of Munich

[Homepage](https://afairbairn.com/)


## Installation

You can install chirpR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AFairbairn/chirpR")
```

## Example

This is a basic example which shows you how to install and use BirdNet:

```{r }
library(chirpR)

## Install BirdNet
birdNet.install()

## Run BirdNet using default settings
## i is the input files path, as in BirdNet-Analyze
results <- birdNet.analyze(i="D:/acoustic recordings")
head(results[,c(4:6)])
```
