---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chirpR: tools for automated acoustic analyses in R

<!-- badges: start -->
```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

```{r, echo = FALSE, results='asis'}
cat(
	badge_lifecycle("experimental", "red"),
	badge_github_actions("Afairbairn/chirpR"),
  badge_repostatus("Active", "green"),
  badge_license("CC BY-NC-SA 4.0")
)
```
<!-- badges: end -->

## Description

`chirpR` is a work in progress. Originally being built for internal use only, I decided that maybe there are others that would benifit from this tool.

`chirpR` is an R package that simplifies the process of analyzing and interpreting bird acoustic monitoring data. It provides a user-friendly wrapper for [BirdNet-Analyzer](https://github.com/kahst/BirdNET-Analyzer) and [ecoVAD](https://github.com/NINAnor/ecoVAD), allowing users to easily install and run BirdNet and ecoVAD directly from R. Additionally, `chirpR` includes a collection of functions for analyzing and visualizing BirdNet output. Developed with a semi-automated analysis pipeline in mind, `chirpR` streamlines the analysis process.

## About

Developed by 🦜Andrew Fairbairn

Current lab: [Chair for Terrestrial Ecology](https://www3.ls.tum.de/en/toek/home/), Technical University of Munich

[Homepage](https://afairbairn.com/)


## Installation

You can install chirpR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AFairbairn/chirpR")
```

`chirpR` requires Python 3.8 <= 3.10
To install a supported version of Python, head over to https://www.python.org/, hover over downloads, select your operating system and then scroll down to the installer for a supported version of python. Download and follow the installation instructions. Be sure at add Python to your systems PATH. This is usually an option during installation, but if not do a search for adding Python to PATH of your particular operating system.

## BirdNet Example

Installing and running BirdNet:

```{r, cache = TRUE}
library(chirpR)

## Install BirdNet
birdNet.install()

## Run BirdNet using default settings
## i is the input files path, as in BirdNet-Analyze
results <- birdNet.analyze(i="E:/acoustic recordings", o="E:/bnResults")
head(results[,c(4:6)])
```


## ecoVAD Example

Setup ecoVAD:

```{r }
library(chirpR)

## Setup ecoVad
#ecoVAD.setup()

```

### Training ecoVAD models

The developers of [ecoVAD](https://github.com/NINAnor/ecoVAD) recommend training using the OpenSLR LibriSpeech English language library. As a service for our users, I thought that I would provide a list to several speech libraries for different languages below. This is not an exhaustive list and I would appreciate submission of additional resources. Just contact me!

* English
    + [LibriSpeech ASR corpus](https://www.openslr.org/12/)
* German
    +[LibriVoxDeEn](https://www.cl.uni-heidelberg.de/statnlpgroup/librivoxdeen/)
    +[LibriVox MP3 bundle](https://www.ce.cit.tum.de/mmk/verschiedenes/german-speech-corpus-aligned-with-ctc-segmentation/)
    
