---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chirpR: Tools for Analyzing and Handling BirdNET Analyse Results

<!-- badges: start -->
```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

```{r, echo = FALSE, results='asis'}
cat(
	badge_lifecycle("experimental", "red"),
	badge_github_actions("Afairbairn/chirpR"),
  badge_repostatus("Active", "green"),
  badge_license("CC BY-NC-SA 4.0")
)
```
<!-- badges: end -->

## Description

`chirpR` is a work in progress. Originally being built for internal use only, I decided that maybe there are others that would benefit from this tool.

`chirpR` is an R package that simplifies the process of preparing, analyzing and interpreting [BirdNET](https://github.com/birdnet-team/BirdNET-Analyzer) results.

### Citation
Fairbairn A (2025). _chirpR: Tools for Analyzing and Handling BirdNET Analyze Results_. R package version 0.2.5, <https://github.com/AFairbairn/chirpR>

```
 @Manual{,
    title = {chirpR: Tools for Analyzing and Handling BirdNET Analyze Results},
    author = {Andrew J. Fairbairn},
    year = {2025},
    note = {R package version 0.2.5},
    url = {https://github.com/AFairbairn/chirpR},
  }
```

## About

Developed by 🦜Andrew J. Fairbairn

Current affiliations:
[RARElab](https://www.rarelab.org/)
[Chair for Terrestrial Ecology](https://www3.ls.tum.de/en/toek/home/), Technical University of Munich

[Homepage](https://afairbairn.com/)

## Installation

You can install chirpR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AFairbairn/chirpR")
```

