---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bnanalysis: [BirdNet-Analyzer](https://github.com/kahst/BirdNET-Analyzer) in R

<!-- badges: start -->
```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

```{r, echo = FALSE, results='asis'}
cat(
	badge_lifecycle("experimental", "red"),
	badge_github_actions("Afairbairn/bnanalysis"),
  badge_repostatus("Active", "green"),
  badge_license("GPL v3.0")
)
```
<!-- badges: end -->

## Description

`bnanalysis` is an R package that simplifies the process of analyzing and interpreting BirdNet data. It provides a user-friendly wrapper for [BirdNet-Analyzer](https://github.com/kahst/BirdNET-Analyzer), allowing users to easily install and run BirdNet directly from R. Additionally, `bnanalysis` includes a collection of functions for analyzing and visualizing BirdNet output. Developed with a semi-automated analysis pipeline in mind, `bnanalysis` streamlines the BirdNet analysis process.

* Features to-do list:
  + Support for operating systems other than Windows.
  + Function to create output tables for, for example, odd detections in Kaleidoscope or other.
  + Function for calculating VAR "Vocal Activity Rate"
  + Visualization functions for the bird community
  

## About

Developed by 🦜Andrew Fairbairn

[Chair for Terrestrial Ecology](https://www3.ls.tum.de/en/toek/home/), Technical University of Munich

[Homepage](https://afairbairn.com/)


## Installation

You can install bnanalysis from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AFairbairn/bnanalysis")
```

## Example

This is a basic example which shows you how to install and use BirdNet:

```{r }
library(bnanalysis)

setwd("D:/myProject")

## Install BirdNet
getBN()

## Run BirdNet using default settings
## i is the input files path, as in BirdNet-Analyze
results <- analyze(i="D:/acoustic recordings")
head(results[,c(4:6)])
```
